---
title: "p8105_hw6_qw2282"
author: "Qinyao Wu"
date: "11/17/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Add packages

library(tidyverse)
library(modelr)
library(mgcv)

```


```{r}
#Import the data and tidy by combing the city and state. 
homicide_data = read_csv("data/homicide-data.csv") %>% 
    mutate(
        city_state = str_c(city, ", ", state),
        resolved = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), 0, 1),
       resolved = as.factor(resolved)
           ) %>% 
  mutate(victim_age = as.numeric(victim_age)) %>% 
  
  #Remove the city states that we do not need. 
  
    filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>% 
  
  #Relevel the races. 
    mutate(
        victim_race = ifelse(victim_race == "White", "white", "non-white"),
        victim_race = factor(victim_race, levels = c("white", "non-white")))

```




```{r}
#Filter the data for baltimore. 

baltimore_df = 
  homicide_data%>% 
   filter(city_state == "Baltimore, MD") 
#%>% 
 # select(resolved, victim_age, cat_race, victim_sex) 

#Fit baltimore data
fit_logistic = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

#tidy the result to add the odds ratios.

fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate), 
         
         # Add the confidence interval
         
         ci_lower = exp(estimate - qnorm(0.975) * std.error),
         ci_upper =  exp(estimate + qnorm(0.975) * std.error)) %>% 
  #Print the tatble
  knitr::kable(digits = 3)

```


```{r}
#Apply the method to all the city states. 
OR_city_state = homicide_data %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(result = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = .x, family = binomial()))) %>%
select(-data) %>%
   #Tidy the result with broom and add the odds ratio and the confidence interval. 
  mutate(result_tidy = map(result, broom::tidy)) %>%
  unnest(result_tidy) %>% 
  mutate(OR = exp(estimate), 
         ci_lower = exp(estimate - qnorm(0.975) * std.error),
         ci_upper =  exp(estimate + qnorm(0.975) * std.error)) %>%
  select(city_state, term, log_OR = estimate, OR, p.value, ci_lower, ci_upper) %>% 
  filter(term == "victim_racenon-white") %>% 
  mutate(city_state = forcats::fct_reorder(factor(city_state), OR)) 

#Plot the OR for all city_states. 

ggplot(OR_city_state, aes( x = city_state, y = OR)) +
  geom_point(aes(size = 5)) +
  
  #Add the error bar. 
  geom_errorbar(aes(x = city_state, ymin = ci_lower, ymax = ci_upper)) +
  theme(text = element_text(size = 8), axis.text.x = element_text(angle = 60, hjust = 1)) + 
  
  #Add the title and the name for x and y axis. 
  labs(
    title = "OR estimation of Different City State of Black People",
    x = "City State",
    y = "Estimation of OR of unsolved Black homicides"
  )
```

###Problem 2

```{r}
#Read the data for birthweight

data_birthweight = read.csv(file = "./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         malform = as.factor(malform),
         frace = as.factor(frace),
         mrace = as.factor(mrace))


```

```{r}
####Build model

###Use stepwise function
mult.fit = lm(bwt ~ ., data = data_birthweight)
step(mult.fit, direction = 'backward')


#Here is my model. 
design_model = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = data_birthweight) 


design_model %>% 
  summary() #R squre = 0.71

data_birthweight %>% 
  add_residuals(model = design_model, var = "resid") %>% 
  add_predictions(model = design_model, var = "pred") %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  geom_smooth() + 
  #Add the title and the name for x and y axis. 
  labs(
    title = "Model Residuals v.s. Fitted Values",
    x = "Prediction values",
    y = "Residuals"
  )

```



####Model proposal

I propose this model by using Stepswise Regression Selection. And by looking at these variables, these variables are meaningful in real life circumstances, especially the baby sex, babylength and gestational age in weeks. They do have a great influence on the infants' weight. In addtion to the meanings, this model also have a high adjusted r squred value, which is 0.71. This indicates that my model explains 71% of the dataset. 

From the plot, we can observe that, when the prediction value is relatively small, usually smaller than 2000, the residual tend to be higher and the model don't have an accurate prediction. When the prediction value is larger than 2000, the residual becomes small and the prediction is accurate. 


```{r}
###Model with birth length and gaweeks
model_2 = lm(bwt ~ blength + gaweeks, data = data_birthweight) %>% 
  broom::tidy()

###Model with three way interaction
model_3 = lm(bwt ~ babysex + bhead + blength + blength * babysex * bhead, data = data_birthweight) %>% 
  broom::tidy()

```


###Comparison between models

```{r}
cv_df = 
  crossv_mc(data_birthweight, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))

#Perform the cross validation and add the rmse by using the test data. 
cv_df = 
  cv_df %>% 
  mutate(model_1    = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = data_birthweight)),
         model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = data_birthweight)),
         model_3 = map(train, ~lm(bwt ~ blength + babysex + bhead + blength * babysex * bhead, data = data_birthweight))) %>% 
  
  mutate(rmse_1   = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
         rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))


#Make the violin plot for three models with thr rmse. 
cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) + 
  geom_violin() + 
  #Add the title and the name for x and y axis. 
  labs(
    title = "Comarison of rmse between three models",
    x = "Models",
    y = "rmse"
  )

```

From the vilin plot of the comparison between three models, we can conclude that the first model is the most superior one, which is the model we designed. 